Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-09-07 paper_comparison/paper_comparison/paper_comparison.Rmd
figure sizing and caption plus annotation for first one

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
```

@@

@@

mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(mod$plot(dat, theme = theme_light()) + ggtitle("Good residuals"),
                      mod$plot(mod$set_prm("include_z", TRUE)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Non-linearity"),
                      mod$plot(heter_model(b = 64)$gen(300, computed = select(dat, x, e)), theme = theme_light()) + ggtitle("Heteroskedasticity"),
                      mod$plot(heter_model(b = 0, e = rand_lognormal(sigma = 0.5))$gen(300, computed = select(dat, x)), theme = theme_light()) + ggtitle("Non-normality"))
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  echo = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "100%")
```

@@

```{r commondepartures, fig.cap = "Example fitted vs residual plots: (A) classically good looking residuals, (B) non-linear pattern indicates that the model has not captured a non-linear association, (C) heteroskedasticity indicating that variance around the fitted model is not uniform, and (D) non-normality where the residual distribution is not symmetric around 0. The latter pattern might best be assessed using a univariate plot of the residuals, but patterns B and C need to be assessed using a residual vs fitted plot."}

@@

mod <- poly_model(include_z = FALSE, sigma = 0.25)
dat <- mod$gen(300)
patchwork::wrap_plots(
  mod$plot(dat, theme = theme_light()) +
    ggtitle("A. Good residuals") + 
    xlab("fitted values") + ylab("residuals"),
  mod$plot(mod$set_prm("include_z", TRUE)$gen(300, 
    computed = select(dat, x, e)), 
    theme = theme_light()) + 
    ggtitle("B. Non-linearity") +
    xlab("fitted values") + ylab("residuals"),
  mod$plot(heter_model(b = 64)$gen(300, 
    computed = select(dat, x, e)), 
    theme = theme_light()) + 
    ggtitle("C. Heteroskedasticity") +
    xlab("fitted values") + ylab("residuals"),
  mod$plot(heter_model(b = 0, 
    e = rand_lognormal(sigma = 0.5))$gen(300, 
    computed = select(dat, x)), 
    theme = theme_light()) + 
    ggtitle("D. Non-normality") +
    xlab("fitted values") + ylab("residuals")
)
```

### 2022-09-07 paper_comparison/paper_comparison/paper_comparison.tex
figure sizing and caption plus annotation for first one

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-6-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-7-1.pdf}

@@

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/residual-plot-cubic-heter-1.pdf}
\caption{Residuals vs.~fitted values plot for a classical linear
regression model. The residuals are produced by fitting a two-predictor
multiple linear regression model with data generated from a cubic linear
model. From the residual plot, ``butterfly shape'' can be observed which
generally would be interpretd as evidence of heteroskedasticity.
Further, from the outline of the shape, nonlinear patterns exist. Both
visual discoveries are evidence against the null hypothesis, though
heteroskedasticity actually does not exist in the data generating
process. \label{fig:residual-plot-cubic-heter}}
\end{figure}

@@

\includegraphics{paper_comparison_files/figure-latex/different-shape-of-herimite-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/different-sigma-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/different-dist-1.pdf}

@@

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/example-lineup-1.pdf}
\caption{Example lineup \label{fig:example-lineup}}
\end{figure}

@@

\includegraphics{paper_comparison_files/figure-latex/different-shape-of-heter-1.pdf}

@@

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/demographic-summary-plot-1.pdf}
\caption{Summary of demographic information.
\label{fig:demographic-summary-plot}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/power-overview-1.pdf}
\caption{Power overview. \label{fig:power-overview}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/dist-power-1.pdf}
\caption{\label{dist-power}}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{paper_comparison_files/figure-latex/shape-power-1.pdf}
\caption{\label{shape-power}}
\end{figure}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-14-1.pdf}

@@

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-17-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-18-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-19-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-20-1.pdf}

\includegraphics{paper_comparison_files/figure-latex/unnamed-chunk-21-1.pdf}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/commondepartures-1} \caption{Example fitted vs residual plots: (A) classically good looking residuals, (B) non-linear pattern indicates that the model has not captured a non-linear association, (C) heteroskedasticity indicating that variance around the fitted model is not uniform, and (D) non-normality where the residual distribution is not symmetric around 0. The latter pattern might best be assessed using a univariate plot of the residuals, but patterns B and C need to be assessed using a residual vs fitted plot.}\label{fig:commondepartures}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-1}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/residual-plot-cubic-heter-1} \caption{Residuals vs. fitted values plot for a classical linear regression model. The residuals are produced by fitting a two-predictor multiple linear regression model with data generated from a cubic linear model. From the residual plot, "butterfly shape" can be observed which generally would be interpretd as evidence of heteroskedasticity. Further, from the outline of the shape, nonlinear patterns exist. Both visual discoveries are evidence against the null hypothesis, though heteroskedasticity actually does not exist in the data generating process. \label{fig:residual-plot-cubic-heter}}\label{fig:residual-plot-cubic-heter}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-shape-of-herimite-1}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-sigma-1}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-dist-1}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/example-lineup-1} \caption{Example lineup \label{fig:example-lineup}}\label{fig:example-lineup}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/different-shape-of-heter-1}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/demographic-summary-plot-1} \caption{Summary of demographic information. \label{fig:demographic-summary-plot}}\label{fig:demographic-summary-plot}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/power-overview-1} \caption{Power overview. \label{fig:power-overview}}\label{fig:power-overview}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/dist-power-1} \caption{\label{dist-power}}\label{fig:dist-power}
\end{figure}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/shape-power-1} \caption{\label{shape-power}}\label{fig:shape-power}
\end{figure}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-13-1}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-16-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-17-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-18-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-19-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-20-1}
